Work Fragmentation in Developer Interaction Data

### 2016-01-26 paper_2.tex
Statistics tables and histograms of sessions merged into one figure

After the transformation phase, we had the sessions in a proper format to carry out the analysis. Some statistics about the sessions in Mylyn can be seen in the Table \ref{tbl:stats_sessions_mylyn}, and the distribution of the productive time of this sessions is shown in the Figure \ref{fig:mylyn_trace_duration}. Both the Table and Figure consider the productive time of the session, that is the total time without considering the time consumed by interruptions. Also, the outliers are ignored by setting a threshold of three times the standard deviation. This filter is used only to show the distribution, to avoid a very long tail provoked by unusually long sessions.

\begin{table}[ht!]
	\small
	\renewcommand{\arraystretch}{1.3}
	\caption{Statistics about the sessions in Mylyn. }
	\label{tbl:stats_sessions_mylyn}
	\centering
	\begin{tabular}{| p{3cm} |p{3cm} |} 
		\hline 
		stat & value \\  
		\hline 
		\hline 
		total & 4,284 \\
		min. & 2 min \\
		1st Qu. & 18 min\\
		median & 35 min \\
		mean & 48.91 min \\
		3rd Qu. & 62 min \\
		max. & 535 min\\
		\hline

\begin{figure}[t]
	\centering
	\begin{tabular}{c}
		\includegraphics[width=0.6\linewidth,clip=, angle=0]{figures/mylyn_trace_duration} 
	\end{tabular}
	\caption{Histogram of the duration of the sessions in Mylyn.}
	\label{fig:mylyn_trace_duration}
\end{figure}

@@

At this point, we had the same format of sessions with both datasets. Some statistics about the sessions can be seen in the Table \ref{tbl:stats_sessions_udc}, and a histogram of the duration of the sessions on UDC is shown in the Figure \ref{fig:hist_session_duration_udc}, which ignores outliers by setting a threshold of three times the standard deviation.

\begin{table}[ht!]
	\small
	\renewcommand{\arraystretch}{1.3}
	\caption{Statistics about the sessions in UDC. }
	\label{tbl:stats_sessions_udc}
	\centering
	\begin{tabular}{| p{3cm} |p{3cm} |} 
		\hline 
		stat & value \\  
		\hline 
		\hline 
		total & 15,825 \\
		min. & 2 min \\
		1st Qu. & 11 min\\
		median & 23 min \\
		mean & 35.87 min \\
		3rd Qu. & 47 min \\
		max. & 1,345 min\\
		\hline

\begin{figure}[t]
	\centering
	\begin{tabular}{c}
		\includegraphics[width=0.6\linewidth,clip=, angle=0]{figures/udc_trace_duration} 
	\end{tabular}
	\caption{Histogram of the duration of the sessions in UDC.}
	\label{fig:hist_session_duration_udc}
\end{figure}

>>>>

After the transformation phase, we had the sessions in a proper format to carry out the analysis. In the Figure \ref{fig:mylyn_sessions_stats} we can observe some statistics (left) about the sessions in Mylyn and the distribution (right) of the productive time. The productive time of the session is the total time without considering the time consumed by interruptions. Also, the outliers are ignored by setting a threshold of three times the standard deviation. This filter is used only to show the distribution, to avoid a very long tail provoked by unusually long sessions.

\begin{figure}
	\centering	
	\begin{minipage}[c]{0.30\linewidth}
		\small
		\centering
			\begin{tabular}{| p{2cm} |p{2cm} |} 
				\hline 
				stat & value \\  
				\hline 
				\hline 
				total & 4,284 \\
				min. & 2 min \\
				1st Qu. & 18 min\\
				median & 35 min \\
				mean & 48.91 min \\
				3rd Qu. & 62 min \\
				max. & 535 min\\
				\hline

			\end{tabular}
	\end{minipage}
	\begin{minipage}[c]{0.60\linewidth}
		\centering
		\includegraphics[width=0.8\linewidth,clip=, angle=0]{figures/mylyn_trace_duration} 
	\end{minipage}
	\caption{Statistics (left) and distribution of the productive time (right) of the sessions in Mylyn}
	\label{fig:mylyn_sessions_stats}
\end{figure}

%\begin{table}[ht!]
%	\small
%	\renewcommand{\arraystretch}{1.3}
%	\caption{Statistics about the sessions in Mylyn. }
%	\label{tbl:stats_sessions_mylyn}
%	\centering
%	\begin{tabular}{| p{3cm} |p{3cm} |} 
%		\hline 
%		stat & value \\  
%		\hline 
%		\hline 
%		total & 4,284 \\
%		min. & 2 min \\
%		1st Qu. & 18 min\\
%		median & 35 min \\
%		mean & 48.91 min \\
%		3rd Qu. & 62 min \\
%		max. & 535 min\\
%		\hline
%		
%	\end{tabular}
%\end{table}
%
%
%\begin{figure}[t]
%	\centering
%	\begin{tabular}{c}
%		\includegraphics[width=0.6\linewidth,clip=, angle=0]{figures/mylyn_trace_duration} 
%	\end{tabular}
%	\caption{Histogram of the duration of the sessions in Mylyn.}
%	\label{fig:mylyn_trace_duration}
%\end{figure}

@@

At this point, we had the same format of sessions with both datasets. In the Figure \ref{fig:udc_sessions_stats} we can see statistics about the sessions (left) and a histogram (right) of the duration of the sessions on UDC, which ignores outliers by setting a threshold of three times the standard deviation.

\begin{figure}
	\centering	
	\begin{minipage}[c]{0.30\linewidth}
		\small
		\centering
		\begin{tabular}{| p{2cm} |p{2cm} |} 
			\hline 
			stat & value \\  
			\hline 
			\hline 
			total & 15,825 \\
			min. & 2 min \\
			1st Qu. & 11 min\\
			median & 23 min \\
			mean & 35.87 min \\
			3rd Qu. & 47 min \\
			max. & 1,345 min\\
			\hline

		\end{tabular}
	\end{minipage}
	\begin{minipage}[c]{0.60\linewidth}
		\centering
		\includegraphics[width=0.8\linewidth,clip=, angle=0]{figures/udc_trace_duration} 
	\end{minipage}
	\caption{Statistics (left) and distribution of the productive time (right) of the sessions in UDC}
	\label{fig:udc_sessions_stats}
\end{figure}

%\begin{table}[ht!]
%	\small
%	\renewcommand{\arraystretch}{1.3}
%	\caption{Statistics about the sessions in UDC. }
%	\label{tbl:stats_sessions_udc}
%	\centering
%	\begin{tabular}{| p{3cm} |p{3cm} |} 
%		\hline 
%		stat & value \\  
%		\hline 
%		\hline 
%		total & 15,825 \\
%		min. & 2 min \\
%		1st Qu. & 11 min\\
%		median & 23 min \\
%		mean & 35.87 min \\
%		3rd Qu. & 47 min \\
%		max. & 1,345 min\\
%		\hline
%		
%	\end{tabular}
%\end{table}
%
%
%
%\begin{figure}[t]
%	\centering
%	\begin{tabular}{c}
%		\includegraphics[width=0.6\linewidth,clip=, angle=0]{figures/udc_trace_duration} 
%	\end{tabular}
%	\caption{Histogram of the duration of the sessions in UDC.}
%	\label{fig:hist_session_duration_udc}
%\end{figure}
